A linear inside-outside algorithm for correcting sequencing errors in structured RNA sequences

### 2012-10-07 Recomb/introduction_RECOMB.tex
fix typos

Here, we expand the range of algorithmic techniques previously introduced with \RNAmutants~\cite{Waldispuhl2008}.
Instead of exploring the full conformational landscape and sample mutants, we develop an inside-outside algorithm that enables us
to explore the complete mutational landscape with a \emph{fixed} secondary structure and to calculate exactly mutational probability values. In addition
to a gain into the numerical precision, this strategy allows us to drastically reduce the computational complexity ($\mathcal{O}(n^3 \cdot k^2)$ for the
original version of  \RNAmutants to $\mathcal{O}(n \cdot k^2)$ for \RNApyro, where $n$ is the size of the sequence and $k$ the number of mutations).

>>>>

Here, we expand the range of algorithmic techniques previously introduced with \RNAmutants~\cite{Waldispuhl2008}.
Instead of exploring the full conformational landscape and sample mutants, we develop an inside-outside algorithm that enables us
to explore the complete mutational landscape with a \emph{fixed} secondary structure and to calculate exactly mutational probability values. In addition
to a gain into the numerical precision, this strategy allows us to drastically reduce the computational complexity ($\mathcal{O}(n^3 \cdot m^2)$ for the
original version of  \RNAmutants to $\mathcal{O}(n \cdot m^2)$ for \RNApyro, where $n$ is the size of the sequence and $m$ the number of mutations).
